\documentclass{article}
\input{common/prelude}

% Macros
\input{common/macros}
\input{questions}

\begin{document}

\title{Matthew Scroggs 2024 Christmas Card Solutions}
\author{Dan Whitman}
\date{}

\maketitle

Link to the online card: \href{https://www.mscroggs.co.uk/blog/112}{https://www.mscroggs.co.uk/blog/112}

\cproblem{1}{1312}{\card@xxiv@i}{
  Clearly the largest available digits of $3$ and $4$ should be in the tens places of our two $2$-digit numbers.
  For the ones place, we get more bang for our buck if we get more of the larger of two numbers.
  Hence, our numbers and answer are $41 \cdot 32 = 1312$.
}

\cproblem{2}{8404148160}{\card@xxiv@ii}{
  As there is no discernible logic to choosing the numbers in the general case, a brute force Python program was used that simply tried every permutation.
  This gives us our numbers and answer of $96 \cdot 87543210 = 8404148160$.
}

\cproblem{3}{1225}{\card@xxiv@iii}{
  Drawing from the 2019, Dec 7 problem, the sum of the coefficients of $(ax + b)^n$ is
  \gath{
    S(a, b, n) = \sum_{k=0}^n \binom{n}{k} a^{n - k} b^k.
  }
  So, for the example, we have
  \gath{
    S(2, 3, 2) = \sum_{k=0}^2 \binom{2}{k} 2^{2 - k} 3^k =  2^2 \cdot 3^0 + 2 \cdot 2^1 \cdot 3^1 + 2^0 \cdot 3^2 = 4 + 12 + 9 = 25
  }
  as expected.
  For the main problem we have our answer:
  \gath{
    S(30, 5, 2) = \sum_{k=0}^2 \binom{2}{k} 30^{2 - k} 5^k =  30^2 \cdot 5^0 + 2 \cdot 30^1 \cdot 5^1 + 30^0 \cdot 5^2 = 900 + 300 + 25 = 1225.
  }
}

\cproblem{4}{177147}{\card@xxiv@iv}{
  From the previous problem, we have our answer as
  \gath{
    S(2, 1, 11) = \sum_{k=0}^{11} \binom{11}{k} 2^{11 - k} 1^k = \sum_{k=0}^{11} \binom{11}{k} 2^{11 - k} = \sum_{k=0}^{11} \binom{11}{k} 2^k = 177147,
  }
  which was calculated using Python.
}

\cproblem{5}{6427}{\card@xxiv@v}{
  It turns out that $41306329 = 6427^2$ and $6427$ is prime.
  Therefore, the only factors of $41306329$ are $1$, $6427$, and $41306329$ itself.
  The geometric mean of these factors is then our answer:
  \gath{
    \sqrt[3]{1 \cdot 6427 \cdot 41306329} = \sqrt[3]{6427 \cdot 6427^2} = \sqrt[3]{6427^3} = 6427
  }
}

\cproblem{6}{8464}{\card@xxiv@vi}{
  We know from the 2021, Dec~1 problem that \emph{only} such number is $92^2 = 8464$.
  This was verified using a brute force Python program.
}

\cproblem{7}{2801}{\card@xxiv@vii}{
  Since $n = 7^4 = 2401$ is a prime factorization, we know that there are $4 + 1 = 5$ factors (including $1$ and itself).
  These factors are exactly the $5$ numbers $f_i = 7^i$ where $0 \leq i \leq 4$.
  Thus, their sum is
  \gath{
    \sum_{i=0}^4 f_i = \sum_{i=0}^4 7^i = \frac{7^5 - 1}{7 - 1} = \frac{16806}{6} = 2801.
  }
  This was verified using Python.
}

\cproblem{8}{170260}{\card@xxiv@viii}{
  From the 2019, Dec~3 problem, we know that this is equivalent to the easier problem of how many square numbers there are between $1$ and $m = 28988500000$.
  Now, the square root of $m$ is a little over $170260$ so that $170260^2$ is less than $m$ but $170261^2$ is over it.
  Therefore, our answer is that there are $170260$ square numbers between $1$ and $m$, namely the numbers $i^2$ where $1 \leq i \leq 170260$.
}

\cproblem{9}{133225}{\card@xxiv@ix}{
  In the 2021, Dec~9 problem, it was found that the sum of the $n$ consecutive integers starting at (and including) $a$ is given by
  \gath{
    \sum_{k=a}^{a+n-1} k = \frac{1}{2} n (n + 2a - 1) \label{eqn:09:sum}
  }
  If we call this sum $s_1$, we of course get
  \gath{
    s_1 = \frac{1}{2} n (n + 2a - 1).
  }
  The first integer after this initial set is of course $a + n$.
  So, if we start here and sum the next $n$ integers, calling this $s_2$, then we can again apply \eqref{eqn:09:sum} to get
  \gath{
    s_2 = \frac{1}{2} n \squares{n + 2(a + n) - 1} = \frac{1}{2} n \squares{3n + 2a - 1}.
  }
  Clearly, $s_2$ will be larger than $s_1$ since every integer in the sum of $s_2$ is larger than those added to make $s_1$.
  Subtracting $s_1$ from $s_2$ then results in the positive integer
  \gath{
    s_2 - s_1 = \frac{1}{2} n \squares{3n + 2a - 1} - \frac{1}{2} n (n + 2a - 1) = \frac{1}{2} n (2n) = n^2.
  }
  Interestingly, this difference is simple and does not depend on the starting integer $a$.
  Eve has $n = 365$ so that her result must be $n^2 = 365^2 = 133225$.
  This was verified using a brute force Python program.
}

\cproblem{10}{4727}{\card@xxiv@x}{
  It was derived in the previous problem that the difference of sums depends only on $n$ and not on the starting number.
  Moreover, this difference is simply $n^2$ so that our answer must be $n = \sqrt{22344529} = 4727$.
}

\end{document}
