\documentclass{article}
\input{common/prelude}

% Macros
\input{common/macros}
\input{questions}
\input{boxes}

\begin{document}

\title{MS Scroggs Advent Calendar 2016 Answers}
\author{Dan Whitman}
\date{}

\maketitle

Answers: \href{https://www.mscroggs.co.uk/puzzles/advent2016}{https://www.mscroggs.co.uk/puzzles/advent2016}

\aproblem{1}{563}{\advent@xvi@i}{
  Suppose that today's number has the three digits $d_2 d_1 d_0$.
  If $d_2$ or $d_1$ were removed then the last digit of the sum would be $d_0 + d_0 = 2d_0$ and so would be even.
  As $9$ is odd, it means that $d_0$ must be the digit that was removed so that the two digit number therefore has digits $d_2 d_1$.
  Thus we have
  \begin{center}
    \begin{tabular}{c@{\,}c@{\,}c@{\,}c}
          & $d_2$ & $d_1$ & $d_0$ \\
      $+$ &       & $d_2$ & $d_1$ \\
      \hline
          & 6     & 1     & 9
    \end{tabular} \,.
  \end{center}
  Moreover, no digits can add to $19$ (since the biggest digit $9 + 9 = 18 < 19$) so that
  \gath{
    d_0 + d_1 = 9 \label{eqn:01:d0d1}
  }
  with no carry to the next digit.
  Since the middle digit of the sum is $1$, either $d_1 + d_2 = 1$ or $d_1 + d_2 = 11$.
  In the former case it has to be that $d_1 = 0$ and $d_2 = 1$ since otherwise the two digit number would actually only be a one digit number.
  However, in this case, it cannot possibly be that the first digit of the sum is $6$.
  So it must be that in fact
  \gath{
    d_1 + d_2 = 11 \label{eqn:01:d1d2}
  }
  so that $d_2 + 1 = 6$ because of the carry, and thus $d_2 = 6 - 1 = 5$.
  Hence $d_1 = 11 - d_2 = 11 - 5 = 6$ by \eqref{eqn:01:d1d2}, from which it follows from \eqref{eqn:01:d0d1} that $d_0 = 9 - d_1 = 9 - 6 = 3$.
  Therefore today's number is $d_2 d_1 d_0 = 563$.
}

\aproblem{2}{435}{\advent@xvi@ii}{
  If they are placed in an optimal way, each time a plane is added, it can intersect every already-placed plane.
  So clearly a single plane has $0$ intersections, adding a second plane adds $1$ intersection, adding a third plane adds $2$ more intersections, etc.
  Thus for $n$ planes the maximum number of intersecting lines is a triangular number:
  \gath{
    f(n) = \sum_{i=1}^{n-1} i = \frac{(n-1)(n-1 + 1)}{2} = \frac{n(n-1)}{2} \,.
  }
  Hence our answer is $f(30) = 435$.
}

\aproblem{3}{798}{\advent@xvi@iii}{
  Clearly the smallest such cube is such that the base of the pyramid is square and coincides with one side of the cube.
  The height of the pyramid then is also the same as the sides of the square base.
  If the sides of the enclosing cube have length $s$, then the base length, base width, and height of the pyramid are all $l = w = h = s$.
  The volume of the pyramid is then
  \gath{
    V_p = \frac{lwh}{3} = \frac{s^3}{3} \,.
  }
  The volume of the cube is of course simply
  \gath{
    V_c = s^3
  }
  so that $V_c = 3 V_p = 3 \cdot 266 = 798$, which is our answer.
}

\aproblem{4}{140}{\advent@xvi@iv}{
  \boxans{\gridsol@advent@xvi@iv}
}

\aproblem{5}{414}{\advent@xvi@v}{
  This was solved using Python.
}

\aproblem{6}{819}{\advent@xvi@vi}{
  Let $S(k)$ denote the digital sum of a non-negative integer $k$.
  We will prove the following set identity:
  \gath{
    \braces{S(k) \mid 1 \leq k \leq 10^n} = \braces{1, 2, \ldots, 9n}\,, \label{eqn:06:hyp}
  }
  for all integers $n \geq 1$.
  We show this by induction on $n$.
  In what follows define $A_n = \braces{S(k) \mid 1 \leq k \leq 10^n}$ and $B_n = \braces{1, 2, \ldots, 9n}$ so that we must show that $A_n = B_n$ for all $n \geq 1$.
  First, for $n = 1$, consider any $x \in A_n$ so that $x = S(k)$ for some $1 \leq k \leq 10^n = 10$.
  If $k$ is a single digit $1$ through $9$ then of course simply $x = S(k) = k$, and if $k = 10$ then of course $x = S(k) = 1$.
  Thus, in any case, $1 \leq x \leq 9 = 9n$ so that $x \in B_n$, and therefore $A_n \ss B_n$.
  Conversely, consider any $x \in B_n$ so that $1 \leq x \leq 9n = 9$ and simply set $k = x$ so that of course $x = S(k) = k$ since it is just a single digit.
  Since also clearly $1 \leq k = x \leq 9 \leq 10 = 10^n$, we have $x \in A_n$ so that $B_n \ss A_n$ as well.

  Now suppose that \eqref{eqn:06:hyp} is true for $n \geq 1$ and consider any $x \in A_{n+1}$ so that $x = S(k)$ for some $1 \leq k \leq 10^{n+1}$.
  If $k < 10^{n+1}$ then $k$ can be considered as an $n$-digit number where the first digit may be zero if $k < 10^n$.
  So let $d$ be the first digit and let $m$ be the integer formed by the remaining digits.
  Therefore $0 \leq d \leq 9$ and $m$ is a nonzero $(n-1)$-digit number and hence $1 \leq m < 10^n$.
  Thus $S(m) \in A_n = B_n$ by the induction hypothesis so that $1 \leq S(m) \leq 9n$.
  Since also clearly $x = S(k) = d + S(m)$, we have
  \gath{
    0 + 1 \leq d + S(m) \leq 9 + 9n \non
    1 \leq S(k) \leq 9(n+1) \non
    1 \leq x \leq 9(n+1)
  }
  so that $x \in B_{n+1}$, and hence $A_{n+1} \ss B_{n+1}$.
  Now suppose that $x \in B_{n+1}$ so that $1 \leq x \leq 9(n+1)$.
  In the case where $1 \leq x \leq 9n$ then $x \in B_n = A_n$ by the induction hypothesis, and so there is a $1 \leq k \leq 10^n$ where $x = S(k)$.
  Since also $1 \leq k \leq 10^n \leq 10^{n+1}$, it follows that $x = S(k) \in A_{n+1}$.
  In the other case where $9n < x \leq 9(n+1)$ set $d = 9$ and $y = x - d$ so that
  \gath{
    9n - 9 < x - 9 \leq 9(n+1) - 9 \non
    9(n-1) < x - d \leq 9n + 9 - 9 \non
    0 \leq 9(n-1) < x - d \leq 9n \non
    1 \leq y \leq 9n \,
  }
  noting that $0 \leq 9(n-1)$ since $1 \leq n$.
  Hence $y \in B_n = A_n$ by the induction hypothesis so that there is a $1 \leq k \leq 10^n$ such that $y = S(k)$.
  Now, if $k = 10^n$, then it must be that $y = S(k) = 1$, so let $m = k + 9 = 10^n + 9$ so that clearly
  \gath{
    1 + 9 \leq k + 9 \leq 10^n + 10 \non
    10 \leq k + 9 \leq 10^{n+1} \non
    1 \leq m \leq 10^{n+1} \,.
  }
  Since we also clearly have $x = y + d = y + 9 = 1 + 9 = 10 = S(10^n + 9) = S(m)$, it follows that $x \in A_{n+1}$.
  Otherwise we have $1 \leq k < 10^n$ so that $k$ is an $(n-1)$-digit number (where leading digits may be zero).
  So let $m$ be the number with leading digit $d = 9$ followed by the digits of $k$, resulting in an $n$-digit number so that $1 \leq m \leq 10^{n+1}$.
  Clearly also $S(m) = 9 + S(k) = 9 + y = d + y = x$.
  Thus we have that $x \in A_{n+1}$ and, as this is true in all cases, it follows that $B_{n+1} \ss A_{n+1}$, which completes the inductive proof of \eqref{eqn:06:hyp}.

  Clearly then our answer is $\abs{A_{91}} = \abs{B_{91}} = \abs{\braces{1, 2, \ldots, 9 \cdot 91}} = 9 \cdot 91 = 819$.
}

\aproblem{7}{691}{\advent@xvi@vii}{
  \boxans{\grid@advent@xvi@vii{3}{7}{5}{6}{9}{1}{4}{8}{2}}
}

\aproblem{8}{TODO}{\advent@xvi@viii}{
  TODO
}

\aproblem{9}{TODO}{\advent@xvi@vix}{
  TODO
}

\aproblem{10}{TODO}{\advent@xvi@x}{
  TODO
}

\aproblem{11}{TODO}{\advent@xvi@xi}{
  TODO
}

\aproblem{12}{TODO}{\advent@xvi@xii}{
  TODO
}

\aproblem{13}{TODO}{\advent@xvi@xiii}{
  TODO
}

\aproblem{14}{TODO}{\advent@xvi@xiv}{
  TODO
}

\aproblem{15}{TODO}{\advent@xvi@xv}{
  TODO
}

\aproblem{16}{TODO}{\advent@xvi@xvi}{
  TODO
}

\aproblem{17}{TODO}{\advent@xvi@xvii}{
  TODO
}

\aproblem{18}{TODO}{\advent@xvi@xviii}{
  TODO
}

\aproblem{19}{TODO}{\advent@xvi@xix}{
  TODO
}

\aproblem{20}{TODO}{\advent@xvi@xx}{
  TODO
}

\aproblem{21}{TODO}{\advent@xvi@xxi}{
  TODO
}

\aproblem{22}{TODO}{\advent@xvi@xxii}{
  TODO
}

\aproblem{23}{TODO}{\advent@xvi@xxiii}{
  TODO
}

\aproblem{24}{TODO}{\advent@xvi@xxiv}{
  TODO
}

\end{document}
