\def\advent@xvi@i{
  One of the digits of today's number was removed to leave a two digit number.
  This two digit number was added to today's number.
  The result was $619$.
}

\def\advent@xvi@ii{
  What is the maximum number of lines that can be formed by the intersection of $30$ planes?
}

\def\advent@xvi@iii{
  What is the volume of the smallest cube inside which a rectangular-based pyramid of volume $266$ will fit?
}

\def\advent@xvi@iv{
  Put the digits $1$ to $9$ (using each digit exactly once) in the boxes so that the sums are correct.
  The sums should be read left to right and top to bottom ignoring the usual order of operations.
  For example, $4 + 3 \times 2$ is $14$, not $10$.
  Today's number is the product of the digits in the red boxes.

  \grid@advent@xvi@iv{}{}{}{}{}{}{}{}{}
}

\def\advent@xvi@v{
  Today's number is the number of ways that 35 can be written as the sum of distinct numbers, with none of the numbers in the sum being divisible by $9$.

  Clarification: By "numbers", I mean (strictly) positive integers.
  The sum of the same numbers in a different order is counted as the same sum: e.g. $1 + 34$ and $34 + 1$ are not different sums.
  The trivial sum consisting of just the number $35$ counts as a sum.
}

\def\advent@xvi@vi{
  When you add up the digits of a number, the result is called the digital sum.

  How many different digital sums do the numbers from $1$ to $10^{91}$ have?
}

\newcommand\grid@advent@xvi@vii[9]{
  \begin{center}
    \begin{tikzpicture}
      \bigbox{0}{3}{#1}
      \bigbox{1}{3}{#2}
      \bigbox{2}{3}{#3}
      \bbtextr{3}{3}{multiple of $25$}

      \bigbox{0}{2}{#4}
      \bigbox{1}{2}{#5}
      \bigbox{2}{2}{#6}
      \bbtextr{3}{2}{today's number}

      \bigbox{0}{1}{#7}
      \bigbox{1}{1}{#8}
      \bigbox{2}{1}{#9}
      \bbtextr{3}{1}{all digits even}

      \bbtextb{0}{0}{multiple\\of $91$}
      \bbtextb{1}{0}{multiple\\of $7$}
      \bbtextb{2}{0}{cube\\number}
    \end{tikzpicture}
  \end{center}
}
\def\advent@xvi@vii{
  Put the digits $1$ to $9$ (using each digit once) in the boxes so that the three-digit numbers formed (reading left to right and top to bottom) have the desired properties written by their rows and columns.

  \grid@advent@xvi@vii{}{}{}{}{}{}{}{}{}
}

\def\advent@xvi@viii{
  Today's number is the second-smallest number that can be written as $a \times b  \times c \times d \times e \times f \times g \times h \times i$, where $a, b, \ldots, i$ are all integers greater than $1$.
}

\def\gs{1}
\newcommand\sizedsqu[4]{
  \draw[thick] (#1 * \gs, #2 * \gs) rectangle (#1 * \gs + #3 * \gs, #2 * \gs + #4 * \gs);
}
\newcommand\smallsqu[2]{
  \sizedsqu{#1}{#2}{1}{1}
}
\def\advent@xvi@ix{
  You start at A and are allowed to move either to the right or upwards.
  \begin{center}
    \begin{tikzpicture}
      % Grid
      \foreach \i in {0,...,2}{
          \foreach \j in {0,...,5}{
              \smallsqu{\i}{\j}
            }
        }
      \foreach \j in {3,...,5}{
          \smallsqu{3}{\j}
        }
      \sizedsqu{3}{0}{3}{3}
      \sizedsqu{6}{0}{3}{3}
      \sizedsqu{4}{3}{3}{3}
      \foreach \i in {7,...,8}{
          \foreach \j in {3,...,5}{
              \smallsqu{\i}{\j}
            }
        }
      \foreach \i in {9,...,11}{
          \foreach \j in {0,...,2}{
              \smallsqu{\i}{\j}
            }
        }
      \sizedsqu{9}{3}{3}{3}

      % Points
      \fill[color=red] (0, 0) circle (0.2) node[color=red,left] {A};
      \fill[color=blue] (12*\gs, 6*\gs) circle (0.2) node[color=blue,right] {B};
    \end{tikzpicture}
  \end{center}
  How many different routes are there to get from A to B?
}

\def\advent@xvi@x{
  The smallest number that is equal to the sum of its digits multiplied by ten more than the sum of its digits.
}

\def\advent@xvi@xi{
  This year, I have spend a lot of time working on the \href{http://avegame.co.uk/}{AVE game engine}.
  Today's answer is the code to the safe in \href{http://avegame.co.uk/play/user/christmas.ave}{this Christmas themed game}.

}

\def\advent@xvi@xii{
  Here is a list of facts about today's number:
  \begin{itemize}
    \item If $a \times b$ is a factor of it, with $a$ and $b$ both positive integers, then either $a$ or $b$ is one.
    \item The sum of its digits is $14$.
    \item It is odd.
    \item The product of its digits is $36$.
    \item It is a palindrome when written in base $9$.
    \item It is smaller than yesterday's number.
    \item It is 4 more than a multiple of $5$.
    \item It is two less than a prime number.
    \item It is the number of a bus stopping at Richmond station.
  \end{itemize}
}

\def\advent@xvi@xiii{
  Put the digits $1$ to $9$ (using each digit exactly once) in the boxes so that the sums are correct.
  The sums should be read left to right and top to bottom ignoring the usual order of operations.
  For example, $4 + 3 \times 2$ is $14$, not $10$.
  Today's number is the smaller number in a red box to the power of the larger number in a red box.

  \grid@advent@xvi@xiii{}{}{}{}{}{}{}{}{}
}

\def\advent@xvi@xiv{
  In July, I posted the \href{http://www.mscroggs.co.uk/puzzles/136}{Combining Multiples} puzzle.

  Today's number is the largest number that cannot be written in the form $27a + 17b$, where $a$ and $b$ are positive integers (or 0).
}

\def\advent@xvi@xv{
  A book has $386$ pages.
  What do the page numbers on the two middle pages add up to?
}

\def\advent@xvi@xvi{
  Put the digits $1$ to $9$ (using each digit exactly once) in the boxes so that the sums are correct.
  The sums should be read left to right and top to bottom ignoring the usual order of operations.
  For example, $4 + 3 \times 2$ is $14$, not $10$.
  Today's number is the largest number than can be made from the digits in red boxes.

  \grid@advent@xvi@xvi{}{}{}{}{}{}{}{}{}
}

\def\advent@xvi@xvii{
  TODO
}

\def\advent@xvi@xviii{
  TODO
}

\def\advent@xvi@xix{
  TODO
}

\def\advent@xvi@xx{
  TODO
}

\def\advent@xvi@xxi{
  TODO
}

\def\advent@xvi@xxii{
  TODO
}

\def\advent@xvi@xxiii{
  TODO
}

\def\advent@xvi@xxiv{
  TODO
}
