\documentclass{article}

\input{common/prelude}

% Macros
\input{common/macros}
\input{questions}
\input{boxes}

\begin{document}

\title{MS Scroggs Advent Calendar 2023 Answers}
\author{Dan Whitman}
\date{}

\maketitle

Magic Link: \href{http://mscroggs.co.uk/adventcode/yglswiTw}{http://mscroggs.co.uk/adventcode/yglswiTw}

\aproblem{1}{180}{\advent@xxiii@i}{
  A regular $n$-gon has interior angles that are each
  \gath{
    \theta = \frac{180(n - 2)}{n}
  }
  in degrees.
  Using basic algebra, solving this for $n$ results in
  \gath{
    n = \frac{360}{180 - \theta}
  }
  Therefore, plugging in $\theta = 178$ gives our answer $n = 180$.
}

\aproblem{2}{681}{\advent@xxiii@ii}{
  Clearly, the sum of the first $n$ even numbers and half of the next even number is
  \ali{
    s_n &= \sum_{i=1}^n 2i + \frac{2(n+1)}{2} = 2 \sum_{i=1}^n i + (n+1) = 2\frac{n(n+1)}{2} + (n+1) \non
    &= n(n+1) = (n+1) = (n+1)^2.
  }
  Solving this for $n$ clearly results in
  \gath{
    n = \sqrt{s_n} - 1.
  }
  Hence, the $n$ we seek is $n = \sqrt{465124} - 1 = 682 - 1 = 681$.
  This answer was verified with a Python program that calculates the actual sum $s_{681}$, showing that this is indeed $465124$.
}

\aproblem{3}{195}{\advent@xxiii@iii}{
  Let $n$ be this smallest multiple of $15$ whose digits add up to $15$.
  First, we note that clearly the digits of $555$ add to $15$, and that $555 = 37 \times 15$, and so is also a multiple of $15$.
  Therefore, it has to be that $n \leq 555$.

  Now, any multiple of $15$ must end in either the digits $0$ or $5$.
  Suppose that the last digit is $0$ so that $n$ has the form $n = d_2 d_10$, and thus $d_2 + d_1 = 15$.
  There are only two sets of digits such that this is the case, namely $6 + 9 = 9 + 6 = 15$ and $7 + 8 = 8 + 7 = 15$.
  This is because $d_2 \leq 5$ would require that $d_1 > 9$ and vice versa.
  Therefore, it has to be that $d_2 \in \braces{6, 7, 8, 9}$, which would mean that $n = d_2 d_1 0 > 555$.
  Hence, it must be that the last digit is a $5$.

  Thus, $n$ has the form $n = d_2 d_1 5$.
  If it were the case that $d_2 = 0$ so that $n$ was a two-digit number, it would have to be that $0 + d_1 + 5 = 15$ so that $d_1 = 10$, which is clearly out of the range of valid digits.
  Therefore, $0 < d_2 \leq 5$.
  What about if $d_2 = 1$?
  Well, in this case, we'd have $1 + d_2 + 5 = 15$ so that $d_2 = 9$.
  Hence, the digits of $n = 195$ sum to $15$.
  Since also $195 = 13 \times 15$, this is in fact our answer since there can be no smaller number that meets the established criteria!

  This answer was also verified using a brute force Python program.
}

\aproblem{4}{246}{\advent@xxiii@iv}{
  Let us generalize this a bit and ask, for any positive integer $a$, what is the largest value of $n$ for which $f(n) = (n! - a)/(n - a)$ is an integer?

  First, for $n = 2a$ we have
  \gath{
    f(n) = f(2a) = \frac{(2a)! - a}{2a - a} = \frac{2a(2a-1)! - a}{a} = 2(2a-1)! - 1,
  }
  which is clearly an integer. We aim to prove that, in fact, $n = 2a$ is the \emph{largest} $n$ for which $f(n)$ is an integer!

  To this end, first note that $f(n)$ being an integer means that $n! - a$ is divisible by $n - a$, which is equivalent to saying that
  \gath{
    n! - a \equiv 0 \pmod{n-a}. \label{eqn:04:fcond}
  }
  Now suppose that $n > 2a$ so that
  \gath{
    a > 0 \non
    n > 2a > a \non
    n - a > a > 0.
  }
  We also clearly have
  \gath{
    n > n - a
  }
  since $a > 0$.
  Therefore, clearly
  \gath{
    n! = (n-a)k,
  }
  where $k$ is an integer.
  Hence, $n!$ is a multiple of $n-a$ so that
  \gath{
    n! \equiv 0 \pmod{n-a}.
  }
  From this it follows that
  \gath{
    n! - a \equiv -a \pmod{n-a},
  }
  and, since $0 < a < n-a$, this means that \eqref{eqn:04:fcond} cannot be true so that $f(n)$ cannot be an integer!

  In our case, we have $a = 123$ so that our answer is $n = 2 \cdot 123 = 246$.
  This answer was also verified using a brute force Python program.
}

\aproblem{5}{378}{\advent@xxiii@v}{
  \boxans{\gridsol@advent@xxiii@v}
}

\newcommand\table@vi[1]{
  \begin{center}
    \begin{tabular}{c|c}
      $n$ & $N_n$ \\
      \hline
      #1
    \end{tabular}
  \end{center}
}
\aproblem{6}{233}{\advent@xxiii@vi}{
  Consider the general problem of the number of ways to tile an $n \times 2$ rectangle with $2 \times 1$ pieces, and let this number be $N_n$.
  Clearly the number of ways to tile a $1 \times 2$ rectangle is just one, and hence $N_1 = 1$.
  Similarly, there are obviously only two ways to tile a $2 \times 2$ square, namely the following:
  \begin{center}
    \begin{tikzpicture}[scale=\vi@scale]
      \vi@vert{vi@y}{0}{0}
      \vi@vert{vi@b}{1}{0}

      \vi@horz{vi@y}{3}{0}
      \vi@horz{vi@b}{3}{-1}
    \end{tikzpicture}
  \end{center}
  Therefore, of course, $N_2 = 2$.

  Now, if we consider $N_n$, we have two cases, either the first $2 \times 1$ tile is oriented vertically or horizontally.
  In the first case, the width of the first tile is only~1 so that the remaining part is an $(n-1) \times 2$ rectangle as shown below:
  \begin{center}
    \begin{tikzpicture}[scale=\vi@scale]
      \vi@vert{vi@y}{0}{0}
      \filldraw[ultra thick,fill=vi@g] (1,0) rectangle (10,-2);
      \node at (6, -1) {$(n-1) \times 2$};
    \end{tikzpicture}
  \end{center}
  Therefore, the number of tilings in this case is simply $N_{n-1}$.
  In the second case in which the first tile is horizontal, the second tile must also be horizontal beneath, and their width is~2 so that the remaining part is an $(n-2) \times 2$ rectangle.
  This is illustrated below:
  \begin{center}
    \begin{tikzpicture}[scale=\vi@scale]
      \vi@horz{vi@y}{0}{0}
      \vi@horz{vi@b}{0}{-1}
      \filldraw[ultra thick,fill=vi@g] (2,0) rectangle (10,-2);
      \node at (6, -1) {$(n-2) \times 2$};
    \end{tikzpicture}
  \end{center}
  Thus, the total number of tilings in this case is $N_{n-2}$.
  As these cases are exhaustive, the total number of tilings is
  \gath{
    N_n = N_{k-1} + N_{k-2},
  }
  but this is just a Fibonacci sequence!
  Putting this all together we clearly have
  \begin{multicols}{3}
    \table@vi{
      1   & 1     \\
      2   & 2     \\
      3   & 3     \\
      4   & 5     \\
    }
    \columnbreak
    \table@vi{
      5   & 8     \\
      6   & 13    \\
      7   & 21    \\
      8   & 34    \\
    }
    \columnbreak
    \table@vi{
      9   & 55    \\
      10  & 89    \\
      11  & 144   \\
      12  & 233   \\
    }
  \end{multicols}
  so that our answer is $N_{12} = 233$, which was verified by implementing this sequence in Python.
}

\newcommand\table@vii[1]{
  \begin{center}
    \begin{tabular}{c|c}
      $n$ & $\abs{C_n}$ \\
      \hline
      #1
    \end{tabular}
  \end{center}
}
\aproblem{7}{987}{\advent@xxiii@vii}{
  For $n \geq 0$, let $I_n$ be the set containing the numbers $1$ to $n$, that is
  \gath{
    I_n = \braces{k \in \ints \mid 1 \leq k \leq n}.
  }
  Similarly, let $C_n$ be the set of subsets of $I_n$ that do not include any consecutive numbers, including the empty set.
  Clearly, we have that $I_0 = \es$, and so $C_0 = \braces{\es}$ and $\abs{C_0} = 1$.
  We also have that $I_1 = \braces{1}$ so that
  \gath{
    C_1 = \braces{\varnothing, \braces{1}},
  }
  and hence $\abs{C_1} = 2$.
  Now consider any $n > 1$ so that $I_n = \braces{1, 2, \ldots, n-1, n}$.
  For any set in $C_n$, either $n$ is in the set or it is not.
  Consider those sets of $C_n$ such that $n$ is \emph{not} in any of the sets.
  The set of these is clearly simply $C_{n-1}$.
  Now consider the sets of $C_n$ where $n$ is in all the sets.
  This means that $n-1$ cannot be in any of the sets since it is consecutive with $n$.
  Thus, these are exactly the sets $\braces{S \cup \braces{n} \mid S \in C_{n-2}}$, which of course has the same cardinality as $C_{n-2}$.
  Since the cases are exhaustive and the set of subsets in each case are clearly disjoint (since none of the sets of one contain $n$ while all the sets of the other contain $n$), it follows that
  \gath{
    \abs{C_n} = \abs{C_{n-1}} + \abs{C_{n-2}}
  }
  so that the sequence $\abs{C_n}$ is a Fibonacci sequence!
  It is then easy to calculate this sequence:
  \begin{multicols}{3}
    \table@vii{
      0   & 1           \\
      1   & 2           \\
      2   & 3           \\
      3   & 5           \\
      4   & 8           \\
    }
    \columnbreak
    \table@vii{
      5   & 13          \\
      6   & 21          \\
      7   & 34          \\
      8   & 55          \\
      9   & 89          \\
    }
    \columnbreak
    \table@vii{
      10  & 144         \\
      11  & 233         \\
      12  & 377         \\
      13  & 610         \\
      14  & 987         \\
    }
  \end{multicols}
  Note hat $\abs{C_4} = 8$ as expected from the example.
  Our answer is then $\abs{C_{14}} = 987$, which was verified using a brute force Python program that filters the power sets of $I_n$ to only those subsets containing non-consecutive integer.
}

\aproblem{8}{729}{\advent@xxiii@viii}{
  Suppose that $n$ is a positive, odd integer so that $n = 2k+1$ for some integer $k \geq 0$.
  Also suppose that we write the inverted triangle of numbers as above where the first row is from $1$ to $n$.
  Since $n$ is odd, there is a number $m$ exactly in the middle of the first row with the property that there are exactly $m-1$ numbers to the left of it (i.e. $1$ through $m-1$) and $m-1$ to the right (i.e. $m+1$ through $n$).
  So the numbers of numbers on the right is
  \gath{
    m - 1 = n - m \non
    2m = n + 1 \non
    2m = (2k + 1) + 1 \non
    2m = 2(k+1) \non
    m = k+1
  }
  so that we have our middle number.
  It should then be clear that there are $m$ rows, and let us number them from $1$ to $m$ from top to bottom, noting that row $r$ starts with the number $r$ and ends with $n - r + 1$.
  The last row then contains only $m = k+1$, noting that the last number is also $n - m + 1 = (2k+1) - (k+1) + 1 = k + 1 = m$.

  A short digression before we proceed: for non-negative integers $a \leq b$, we have that
  \gath{
    \sum_{i=a}^b i = \sum_{i=1}^b i - \sum_{i=1}^{a-1} i = \frac{b(b+1)}{2} - \frac{(a-1)a}{2} = \frac{b(b+1) - a(a-1)}{2}. \label{eqn:08:sumcons}
  }
  This still holds if $a = 0$ if we adopt the usual convention that $\sum_{i=a}^b f(i) = 0$ whenever $b < a$.
  So we then have that the sum of the numbers in row $r$ is
  \ali{
    S_r &= \sum_{i=r}^{n-r+1} i = \sum_{i=r}^{(2k+1)-r+1} i = \sum_{i=r}^{2(k+1)-r} i = \sum_{i=r}^{2m-r} i = \frac{(2m - r)(2m - r + 1) - r(r-1)}{2} \non
    &= \frac{4m^2 - 2m r + 2m - 2m r + r^2 - r - r^2 + r}{2} = \frac{4m^2 - 4m r + 2m}{2} = \frac{2m(2m - 2r + 1)}{2} \non
    &= m(2m - 2r + 1)
  }
  The total sum of all rows is then
  \ali{
    S &= \sum_{r=1}^m S_r = \sum_{r=1}^m m(2m - 2r + 1) = m\squares{\sum_{r=1}^m(2m + 1) - 2\sum_{r=1}^m r} \non
    &= m \squares{m(2m + 1)- 2\frac{m(m+1)}{2}} = m^2 \squares{2m + 1 - (m+1)} = m^3 \non
    &= (k+1)^3.
  }
  In our case, we have that $n = 17 = 2 \cdot 8 + 1$ so that $k = 8$.
  Thus, the sum we seek is $S = (k+1)^3  = 9^3 = 729$.
  This answer was verified with a brute force Python program that calculates the sum directly.
}

\aproblem{9}{600}{\advent@xxiii@ix}{
  Consider the more general case when the length of the red lines is $a$, which is also the length of the blue lines.
  Let $w$ and $h$ denote the width and height of the rectangle, respectively.
  Then the sum of the blue lines is of course
  \gath{
    w + h = a. \label{eqn:09:add}
  }
  One corner of the rectangle along with one of the red lines forms a right triangle with sides $w/2$ and $h$, and a hypotenuse of $a/2$.
  Thus, we have
  \gath{
    \parens{\frac{w}{2}}^2 + h^2 = \parens{\frac{a}{2}}^2 \non
    \frac{w^2}{4} + h^2 = \frac{a^2}{4} \non
    w^2 + 4h^2 + a^2. \label{eqn:09:tri}
  }
  From \eqref{eqn:09:add} we have $w = a - h$, so substituting this into \eqref{eqn:09:tri} gives us
  \gath{
    (a - h)^2 + 4h^2 = a^2 \non
    a^2 - 2ah + h^2 + 4h^2 = a^2 \non
    5h^2 - 2ah = 0 \non
    5h^2 = 2ah \non
    h = \frac{2a}{5}
  }
  Substituting this back into \eqref{eqn:09:add} yields
  \gath{
    w + \frac{2a}{5} = a \non
    w = a\parens{1 - \frac{2}{5}} \non
    w = \frac{3a}{5}.
  }
  Hence, the area is
  \gath{
    A = wh = \parens{\frac{3a}{5}}\parens{\frac{2a}{5}} = \frac{6a^2}{25}.
  }
  In our case, we have $a = 50\unit{cm}$, and therefore our answer is $A = 6 \cdot 50^2/25 = 600\unit{cm^2}$.
}

\aproblem{10}{450}{\advent@xxiii@x}{
  Let $E$ be any even number and $O$ be any odd number.
  It is trivial to show that
  \gath{
    E + E = E \\
    E + O = O + E = O \\
    O + O = E.
  }
  Now note that clearly the sum of the digits of $1000$ is one and so odd, so we need only consider three-digit numbers where the first digit is nonzero.
  There are $5$ even digits (i.e. $\braces{0, 2, 4, 6, 8})$ and $5$ odd digits (i.e. $\braces{1,3,5,7,9}$).
  However, the first digit must be nonzero, so that there are only $4$ possible even number that can be in this position.

  We consider all combinations of whether each digit is even or odd, and denote the parity of each position.
  For example a parity signature of $EOE$ would denote a number where the first digit is even, the second odd, and the third even.
  Note that two sets of numbers with different parity signatures are disjoint since the sets of even and odd digits are disjoint.
  For signatures whose digits sum to an even number, we also calculate the number of such numbers by considering the number of possibilities of each digit given the caveat about the first digit when even.
  Hence, given the addition rules above, we have
  \begin{center}
    \begin{tabular}{ccc}
      Signature & Digital sum & Number of numbers         \\
      \hline
      $EEE$     & $E$         & $4 \cdot 5 \cdot 5 = 100$ \\
      $EEO$     & $O$         &                           \\
      $EOE$     & $O$         &                           \\
      $EOO$     & $E$         & $4 \cdot 5 \cdot 5 = 100$ \\
      $OEE$     & $O$         &                           \\
      $OEO$     & $E$         & $5 \cdot 5 \cdot 5 = 125$ \\
      $OOE$     & $E$         & $5 \cdot 5 \cdot 5 = 125$ \\
      $OOO$     & $O$         &                           \\
    \end{tabular}
  \end{center}
  Therefore, the total number of numbers with even digital sums is the sum of the numbers in the final column: $100 + 100 + 125 + 125 = 450$.
  This result was verified with a brute force Python program.
}

\aproblem{11}{120}{\advent@xxiii@xi}{
  \boxans{\gridsol@advent@xxiii@xi}
}

\aproblem{12}{250}{\advent@xxiii@xii}{
  This was solved using a Python program that deals with these extremely large numbers in terms of their prime factors.
  The prime factors and their exponents are represented as a multiset in which the distinct prime factors are the members and their exponents are the multiplicities.
  If $a$ is a positive integer, let $M(a)$ denote its prime factor multiset.
  The integer operations and properties needed to solve this are equivalent to the following for their multiset representations.
  \begin{center}
    \begin{tabular}{cc}
      Integer operation/property & Multiset operation/property                  \\
      \hline
      $a \cdot b$                & $M(a) \cup M(b)$                             \\
      $a$ divides $b$            & $M(a) \ss M(b)$                              \\
      $a / b$                    & $M(a) - M(b)$ (if $b$ divides $a$)           \\
      $a^b$                      & Multiply all multiplicities of $M(a)$ by $b$ \\
      $a$ is a square number     & All members of $M(a)$ have even multiplicity \\
    \end{tabular}
  \end{center}
  The program then simply does the following:
  \begin{enumerate}
    \item Calculate the prime factor multiset $M(a)$ for $a = 500! \times 499! \times 498! \times \cdots \times 1!$.
    \item For increasing $n$ starting at $n = 100$, calculate $M(n!)$.
    \item If $n$ divides $a$, then calculate $b = a / b$, all using $M(a)$ and $M(n!)$.
    \item If $b$ was calculated and found to be a square number (by testing $M(b)$), then $n$ is printed and the program exits.
    \item Otherwise, jump back to step~2 for the next $n$.
  \end{enumerate}

  TODO: See if we can do prove this analytically, using $x = 250$ and dealing with pairs $(x-1)!(x+1)!$.
}

\aproblem{13}{812}{\advent@xxiii@xiii}{
  \boxans{\crossnumstd{8}{1}{2}{7}{6}{5}{6}{2}{3}}
}

\aproblem{14}{399}{\advent@xxiii@xiv}{
  First, define
  \ali{
    g(x) &= -x^3 + 2x^2 + 6x - 9 \\
    h(x) &= x^2 - 2x + 3
  }
  So that $g(x) \leq f(x) \leq h(x)$ when $0 \leq x \leq 3$.
  Next, let us have a look at $g$ and $h$ in this range:
  \newcommand\plot@xiv[1]{
    \begin{center}
      \begin{tikzpicture}[scale=1.8]
        \begin{axis}[
            axis lines=middle,
            xmin=0, xmax=3,
            ymin=-9, ymax=6,
            samples=100,
          ]
          \addplot[
            blue,
            thick,
            domain=0:3,
          ]
          (x, x^2 - 2*x + 3);
          \node [above] at (axis cs:1,2) {$h$};
          \addplot[
            red,
            thick,
            domain=0:3,
          ]
          (x, -x^3 + 2*x^2 + 6*x - 9);
          \node [below right] at (axis cs:1,-2) {$g$};
          #1
        \end{axis}
      \end{tikzpicture}
    \end{center}
  }
  \plot@xiv{}

  It appears as though these intersect at around $x = 2$.
  Indeed, plugging in, we find that $g(2) = 3 = h(2)$.
  From this, it is immediately clear that it must be that
  \gath{
    f(2) = 3 \label{eqn:14:f2}
  }
  as well since $0 \leq 2 \leq 3$ so that $3 = g(2) \leq f(2) \leq h(2) = 3$.
  Since $g$ and $h$ touch at $(2, 3)$, we would expect their slopes here to be equal such that they only touch at this single point.
  Indeed, we clearly have
  \ali{
    g'(x) &= -3x^2 + 4x + 6 \\
    h'(x) &= 2x - 2
  }
  so that $g'(2) = 2 = h'(2)$.
  It then follows that of course $f$ must have the same slope here as well:
  \gath{
    f'(2) = 2.
  }
  Since $f(x) = ax + b$, it follows that $f'(x) = a$ so that
  \gath{
    f'(2) = a = 2.
  }
  We can then use \eqref{eqn:14:f2} to find $b$:
  \gath{
    f(2) = 2 \cdot 2 + b = 3 \non
    4 + b = 3 \non
    b = -1.
  }
  Therefore, we have $f(x) = 2x - 1$.
  Plotting this along with $g$ and $h$ illustrates that the inequality holds:
  \plot@xiv{
    \addplot[
      black,
      thick,
      domain=0:3,
    ]
    (x, 2*x - 1);
    \node [above left] at (axis cs:0.5,0) {$f$};
  }
  Hence, our answer is $f(200) = 2 \cdot 200 - 1 = 399$.
}

\aproblem{15}{444}{\advent@xxiii@xv}{
  Let $n$ be the number we seek, which we know has the form $4d_1 d_0$, where $d_1$ and $d_0$ are the second and third digits, respectively.
  Since the arithmetic mean of the digits of $n$ is a non-zero integer, we have
  \gath{
    \frac{1}{3}\parens{4 + d_1 + d_0} = k \non
    4 + d_1 + d_0 = 3k \non
    d_1 + d_0 = 3k - 4
  }
  for non-zero integer $k$.
  However, this is equivalent to saying that
  \gath{
    d_1 + d_0 \equiv -4 \equiv 2 \pmod{3}. \label{eqn:15:mod}
  }
  Similarly, the geometric mean is also a non-negative integer so that
  \gath{
    \sqrt[3]{4 \cdot d_1 \cdot d_0} = m \non
    4 \cdot d_1 \cdot d_0 = m^3 \label{eqn:15:mult}
  }
  for some non-zero integer $m$.

  Now, if either of $d_1$ or $d_0$ are zero, then clearly the geometric mean will be zero so that we must have $1 \leq d_1,d_0 \leq 9$ and, hence, we have
  \gath{
    1 \leq d_1 \cdot d_0 \leq 81 \non
    4 \leq 4 \cdot d_1 \cdot d_0 \leq 324 \non
    4 \leq m^3 \leq 324
  }
  Cubic numbers that meet this criterion are $m^3 \in \braces{8, 27, 64, 125, 216}$
  Moreover, by \eqref{eqn:15:mult}, it must be that $m^3$ is a multiple of $4$, which whittles this list down to $m^3 \in \braces{8, 64, 216}$.
  Dividing by $4$, this requires that $d_1 \cdot d_0 \in \braces{2, 16, 54}$.
  Given the factors of these, we can generate the following table:
  \begin{center}
    \begin{tabular}{cccc}
      $m^3$ & $\braces{d_1, d_0}$ & $d_1 + d_0$ & $d_1 + d_0 \pmod{3}$ \\
      \hline
      $2$   & $\braces{1, 2}$     & $3$         & $0$                  \\
      $16$  & $\braces{2, 8}$     & $10$        & $1$                  \\
      $16$  & $\braces{4}$        & $8$         & $2$                  \\
      $54$  & $\braces{6, 9}$     & $15$        & $0$                  \\
    \end{tabular}
  \end{center}
  So, by \eqref{eqn:15:mod}, the only viable option is $d_1 = d_0 = 4$ so that our answer is $n = 444$.
  Verifying, we indeed have the digital means of
  \ali{
    \frac{1}{3}\parens{4 + 4 + 4} = \frac{12}{3} = 4 \\
    \sqrt[3]{4 \cdot 4 \cdot 4} = \sqrt[3]{64} = 4
  }
  as required.
  This answer was verified with a brute force Python program.
}

\aproblem{16}{128}{\advent@xxiii@xvi}{
  We claim that those numbers that cannot be written as the sum of two or consecutive positive integers are exactly the powers of two.
  To see this, first note that the sum of $n$ consecutive numbers starting at $a$ is
  \ali{
    c(a, n) &= \sum_{i=a}^{a+n-1} i = \frac{1}{2}\squares{(a + n - 1)(a + n) - a(a - 1)} = \frac{1}{2}\squares{a^2 + an + an + n^2 - a - n - a^2 + a} \non
    &= \frac{1}{2}\squares{n^2 + (2a-1)n} = \frac{1}{2}n\squares{n + 2a - 1},
  }
  where we have used \eqref{eqn:08:sumcons} derived in the Dec~8 solution above.
  For any positive integer $m$, clearly $m$ can be written as the sum of two or more consecutive integers if and only if there are integers $n > 1$ and $a > 0$ such that
  \gath{
    c(a, n) = m \non
    \frac{1}{2}n\squares{n + 2a - 1} = m \non
    n\squares{n + 2a - 1} = 2m \label{eqn:16:factors}
  }
  so that $n$ and $n + 2a - 1$ must be factors of $2m$.

  Now, suppose that $m = 2^k$ is a power of two and assume that this can be written as the sum of two or more consecutive integers so that \eqref{eqn:16:factors} holds for some $n > 1$ and $a > 0$.
  Then clearly $2m = 2^{k+1}$ can only have even factors, and hence $n$ must be even by \eqref{eqn:16:factors}.
  However, since $n$ is even, it means that $n + 2a - 1$ is odd since clearly $2a - 1$ is odd.
  As this must be another factor of $2m$ by \eqref{eqn:16:factors}, which has to be even, this shows that $m$ cannot be written as the sum of two or more consecutive integers since assuming so results in a contradiction.

  Now suppose that $m > 1$ is \emph{not} a power of two so that $m$ must have a prime factor greater than two, say $k > 2$, which must of course be odd since $2$ is the only even prime.
  Then let $l = m/k > 0$ be another factor of $m$, which may be even or odd.
  Note that $k$ is odd and clearly $2l > 1$ is even so that it must be that $2l \neq k$.
  Thus, we have the following exhaustive cases:

  Case: $2l < k$.
  Then, since $k$ is odd and $2l$ is even, it follows that $\D = k - 2l > 0$ is odd.
  Then set
  \gath{
    a = \frac{\D + 1}{2} = \frac{k - 2l + 1}{2},
  }
  which is a positive integer since $\D > 0$ is odd so that $\D + 1$ is even.
  We then have
  \gath{
    c(a, 2l) = \frac{1}{2}(2l)\squares{2l + 2a - 1} = l\squares{2l + 2\frac{k - 2l + 1}{2} - 1} = l\squares{2l + k - 2l + 1 - 1} = lk = m.
  }
  Thus the $2l$ consecutive integers starting with $a$ sum to $m$.

  Case: $2l > k$.
  Let $\D = 2l - k > 0$, which is odd since $2l$ is even but $k$ is odd.
  Then set
  \gath{
    a = \frac{\D + 1}{2} = \frac{2l - k + 1}{2},
  }
  which is a positive integer since $\D > 0$ is odd so that $\D + 1 > 1$ is even.
  Hence, we have
  \gath{
    c(a, k) = \frac{1}{2}k\squares{k + 2a - 1} = \frac{1}{2}k\squares{k + 2\frac{2l - k + 1}{2} - 1} = \frac{1}{2}k\squares{k + 2l - k + 1 - 1} = \frac{1}{2}k\squares{2l} = lk = m
  }
  so that the $k$ positive integers starting with $a$ sum to $m$.

  Therefore, we have shown that our numbers of interest are exactly the powers of two:
  \gath{
    \braces{2, 4, 8, 16, 32, 64, 128, 256, 512, 1024, \ldots}
  }
  Clearly then, the smallest such three-digit number is our answer $128$.

}

\aproblem{17}{252}{\advent@xxiii@xvii}{
  This problem was solved generally in the 2020, Dec~18 advent problem, in which it was deduced that the number of terms $N(n, k)$ of $(x_1 + \cdots + x_n)^k$ is
  \gath{
    N(n, k) = \binom{n + k - 1}{k},
  }
  where of course the right side is a binomial coefficient.
  So, in our case, the answer is
  \gath{
    N(6, 5) = \binom{6 + 5 - 1}{5} = \binom{10}{5} = \frac{10!}{5!(10-5)!} = \frac{10!}{(5!)^2} = 252.
  }
}

\aproblem{18}{110}{\advent@xxiii@xviii}{
  We can step through numbers manually and investigate products of consecutive factors, if there are any.
  In the below, consecutive factors are in boldface, noting that we disregard the trivial factor of $1$:
  \begin{center}
    \begin{tabular}{clc}
      Number & Factors                                                       & Consecutive products                                   \\
      \hline
      $100$  & $\braces{1, 2, \textbf{4, 5}, 10, 20, 25, 50, 100}$           & $4 \cdot 5 = 20$                                       \\
      $101$  & $\braces{1, 101}$                                             &                                                        \\
      $102$  & $\braces{1, \textbf{2, 3}, 6, 17, 34, 51, 102}$               & $2 \cdot 3 = 6$                                        \\
      $103$  & $\braces{1, 103}$                                             &                                                        \\
      $104$  & $\braces{1, 2, 4, 8, 13, 26, 52, 104}$                        &                                                        \\
      $105$  & $\braces{1, 3, 5, 7, 15, 21, 35, 105}$                        &                                                        \\
      $106$  & $\braces{1, 2, 53, 106}$                                      &                                                        \\
      $107$  & $\braces{1, 107}$                                             &                                                        \\
      $108$  & $\braces{1, \textbf{2, 3, 4}, 6, 9, 12, 18, 27, 36, 54, 108}$ & $2 \cdot 3 = 6,3 \cdot 4 = 12, 2 \cdot 3 \cdot 4 = 24$ \\
      $109$  & $\braces{1, 109}$                                             &                                                        \\
      $110$  & $\braces{1, 2, 5, \textbf{10, 11}, 22, 55, 110}$              & $10 \cdot 11 = 110$                                    \\
    \end{tabular}
  \end{center}
  Thus, clearly our answer is $110$.
  This was verified with a Python program that automates this manual process.
}

\aproblem{19}{504}{\advent@xxiii@xix}{
  \boxans{\gridsol@advent@xxiii@xix}
}


\aproblem{20}{240}{\advent@xxiii@xx}{
  Let $N(k, n)$ be the number of different ways that balls labelled $1$ to $n$ can be put into $k \geq 1$ boxes so that no box is empty.
  This is only valid when $n \geq k$ since, otherwise, at least one of the boxes would have to be empty.
  We develop a recursive formula for $N(k, n)$.
  First, there is clearly only single way to put $n$ balls in a single box (i.e. to put all the balls in the box), and thus $N(1, n) = 1$.
  Now consider the first box.
  This box can contain from $1$ to $n-k+1$ balls to ensure that the remaining boxes will contain at least one ball.
  The number of ways to select $m$ balls from a choice of $n$ balls (where order does not matter) is of course the number of combinations, that is
  \gath{
    \combos{n}{m} = \binom{n}{m},
  }
  the binomial coefficient.
  Now, for each way to choose $m$ balls to put in the first box, then there are $n-m$ balls to put into the remaining $k-1$ boxes, and there are of course $N(k-1, n-m)$ ways to do this.
  Therefore, we have the following recursive formula:
  \gath{
    N(1, n) = 1 \non
    N(k, n) = \sum_{m=1}^{n-k+1} \combos{n}{m} \cdot N(k-1, n-m) = \sum_{m=1}^{n-k+1} \binom{n}{m} N(k-1, n-m). \label{eqn:20:rec}
  }
  There does not seem to be an easy way to reduce or derive a closed form for this.
  Hence, this recursive formula was implemented in Python and verified to match a brute force algorithm that generates the specific bin combinations and counts them.
  Our answer is then $N(4, 5) = 240$.

  We note that the number of ways of choosing $p_i$ balls to put into the $i$th bin for all bins $1 \leq i \leq k$ (and $k$ is the number of bins) is the multinomial coefficient:
  \gath{
    \binom{n}{p_1,\ldots,p_m} = \frac{n!}{p_1! p_2! \cdots p_k!},
  }
  where $p_1 + p_2 + \cdots + p_k = n$.
  However, this does not simplify our problem, but merely shifts the complexity to dealing with all the ways to create the sum $n$ with $k$ positive integers.
  This alternate solution can be expressed by
  \gath{
    N(k, n) = \sum_{p_1 + p_2 + \cdots + p_k = n} \binom{n}{p_1,\ldots,p_m},
  }
  but this is more difficult to actually evaluate than the recursive formula given by \eqref{eqn:20:rec} on account of needing to generate all the sums $p_1 + p_2 + \cdots + p_k = n$.

  TODO: Can this be done with a closed form by first consider all the ways to fill each box with a single ball, then ways to distribute the extra balls, accounting for double counting if necessary?
  Can verify against the current recursive solution at first.
}

\aproblem{21}{231}{\advent@xxiii@xxi}{
  Let $N(n, k)$ be the number of $n$-digit numbers whose digits are all $1$ through $k$, and whose second digit onwards are less than or equal to the previous digit.
  Of course, it must be that $1 \leq k \leq 9$, and we are specifically interested in $k = 3$, but we can derive a more general formula.
  Clearly there are $N(1, k) = k$ such single-digit numbers, which will serve as our base case.
  Now consider an $n$-digit number.
  The first digit $d$ can be $1$ through $k$, and, for each the there are then $N(n-1, d)$ $(n-1)$-digit numbers to fill out the remaining digits since the remaining digits can be no larger than $d$.
  This gives rise to the following recursive formula:
  \gath{
    N(n, k) = \sum_{d=1}^k N(n-1, d).
  }
  Clearly, we then have
  \gath{
    N(2, k) = \sum_{d_1=1}^k N(1, d_1) = \sum_{d_1=1}^k d_1 = \frac{k(k+1)}{2},
  }
  which are the triangular numbers.
  We also have
  \ali{
    N(3, k) &= \sum_{d_2=1}^k N(2, d_2) = \sum_{d_2=1}^k \sum_{d_1=1}^{d_2} d_1 \\
    N(4, k) &= \sum_{d_3=1}^k N(3, d_3) = \sum_{d_3=1}^k \sum_{d_2=1}^{d_3} \sum_{d_1=1}^{d_2} d_1.
  }
  Then, generally,
  \gath{
    N(n, k) = \sum_{d=1}^k N(n-1, d) = \sum_{d_{n-1}=1}^k \sum_{d_{n-2}=1}^{d_{n-1}} \cdots \sum_{d_2=1}^{d_3} \sum_{d_1=1}^{d_2} d_1 = \binom{k + n - 1}{n} = \frac{(k+n-1)!}{n!(k-1)!},
  }
  which is a known formula that generalizes triangular numbers.
  Our answer is then of course
  \gath{
    N(20, 3) = \frac{22!}{20!2!} = \frac{22 \cdot 21}{2} = 231.
  }
}

\def\xxii@octrad{3}
\def\xxii@octlabelrad{0.9*\xxii@octrad}
\newcommand\xxii@oct[1]{
  \begin{tikzpicture}
    % Octogon
    \foreach \th in {0,...,7}{
        \coordinate (A) at (22.5 + \th*45:\xxii@octrad);
        \coordinate (B) at (22.5 + \th*45 + 45:\xxii@octrad);
        \draw[black,thick] (A) -- (B);
        \xxii@dot{A}{white}
        \xxii@dot{B}{white}
      }

    % Side labels
    \node[left] at (180:\xxii@octlabelrad) {$s_1$};
    \node[above left] at (180-45:\xxii@octlabelrad) {$s_2$};
    \node[above] at (180-90:\xxii@octlabelrad) {$s_3$};
    \node[above right] at (180-135:\xxii@octlabelrad) {$s_4$};
    \node[right] at (0:\xxii@octlabelrad) {$s_1'$};
    \node[below right] at (-45:\xxii@octlabelrad) {$s_2'$};
    \node[below] at (-90:\xxii@octlabelrad) {$s_3'$};
    \node[below left] at (-135:\xxii@octlabelrad) {$s_4'$};

    #1

    % Cut line
    \draw[black,thick,dashed] (180+22.5:1.5*\xxii@octrad) -- (22.5:1.5*\xxii@octrad);
  \end{tikzpicture}
}
\newcommand\xxii@octsquare[4]{
  % Rectangle
  \coordinate (A) at (202.5-45*#1:\xxii@octrad);
  \coordinate (B) at (202.5-45*#2:\xxii@octrad);
  \coordinate (C) at (202.5-45*#3:\xxii@octrad);
  \coordinate (D) at (202.5-45*#4:\xxii@octrad);
  \filldraw[black,thick,fill=xxii@purp] (A) -- (B) -- (C) -- (D) -- cycle;
  \draw[blue,ultra thick] (A) -- (B);

  % Dots
  \xxii@dot{A}{xxii@purp}
  \xxii@dot{B}{xxii@purp}
  \xxii@dot{C}{xxii@purp}
  \xxii@dot{D}{xxii@purp}
}
\aproblem{22}{172}{\advent@xxiii@xxii}{
  Right triangles can only be formed from points that define a rectangle, a single rectangle forming $4$ right triangles as in the example.
  So the question can be rephrased as how many rectangles can be formed from the vertices of a regular $n$-gon?
  It seems that $n$-gons with odd $n$ can form no rectangles, and therefore also no right triangles, on account of having no two sides that are parallel.

  So, suppose that $n = 2k$ is an $n$-gon with an even number of sides, and label the half of the adjacent sides from $s_1$ to $s_k$ in order, going around the polygon.
  Since the polygon is even, each side $s_i$ will have an opposite, parallel side $s_i'$, where of course $1 \leq i \leq k$.
  This effectively cuts the $n$-gon into two similar halves.
  This all illustrated below for an octagon:
  \begin{center}
    \xxii@oct{}
  \end{center}
  Now, a circumscribed rectangle within the $n$-gon can be effectively defined by connecting the very first vertex with any of the $k-1$ other vertices in the main half, ignoring the vertex opposite to the very first vertex since this does not create a rectangle.
  The rest of the rectangle is then determined such that the center of the rectangle coincides with the center of the $n$-gon.
  For each of these, there are $k$ ways to rotate the rectangle around the $n$-gon before we start duplicating rectangles.
  Let $1 \leq i \leq k-1$ index which of the other vertices to which the first is connected, and $j$ index the $k$ rotations of the rectangles.
  These $k(k-1)$ rectangles are illustrated below for the $k=4$ octagon, in which the main defining line segment is highlighted:
  \begin{center}
    \begin{tabular}{cccc}
      $i=1$, $j=1$ & $i=1$, $j=2$ & $i=1$, $j=3$ & $i=1$, $j=4$ \\
      \xxii@oct{
        \xxii@octsquare{0}{1}{4}{5}
      }
                   &
      \xxii@oct{
        \xxii@octsquare{1}{2}{5}{6}
      }
                   &
      \xxii@oct{
        \xxii@octsquare{2}{3}{6}{7}
      }
                   &
      \xxii@oct{
        \xxii@octsquare{3}{4}{7}{8}
      }                                                         \\
      $i=2$, $j=1$ & $i=2$, $j=2$ & $i=2$, $j=3$ & $i=2$, $j=4$ \\
      \xxii@oct{
        \xxii@octsquare{0}{2}{4}{6}
      }
                   &
      \xxii@oct{
        \xxii@octsquare{1}{3}{5}{7}
      }
                   &
      \xxii@oct{
        \xxii@octsquare{2}{4}{6}{8}
      }
                   &
      \xxii@oct{
        \xxii@octsquare{3}{5}{7}{9}
      }                                                         \\
      $i=3$, $j=1$ & $i=3$, $j=2$ & $i=3$, $j=3$ & $i=3$, $j=4$ \\
      \xxii@oct{
        \xxii@octsquare{0}{3}{4}{7}
      }
                   &
      \xxii@oct{
        \xxii@octsquare{1}{4}{5}{8}
      }
                   &
      \xxii@oct{
        \xxii@octsquare{2}{5}{6}{9}
      }
                   &
      \xxii@oct{
        \xxii@octsquare{3}{6}{7}{10}
      }                                                         \\
    \end{tabular}
  \end{center}
  The astute observer will notice that, regarding distinct rectangles, there are still duplicates here.
  For example, the $i=1, j=4$ rectangle is the same as the $i=3,j=1$ rectangle, and the $i=2,j=2$ rectangle is the same as the $i=2,j=4$ rectangle.
  In fact, we have counted each distinct rectangle exactly twice!

  Therefore, the number of distinct rectangles is
  \gath{
    N_r(k) = \frac{k(k-1)}{2},
  }
  noting that these are the triangular numbers.
  Since each rectangle forms $4$ right triangles, a regular polygon with $n = 2k$ sides can form exactly
  \gath{
    N_t(k) = 4 N_r(k) = 4\frac{k(k-1)}{2} = 2k(k-1)
  }
  right triangles.

  Thus, for the polygon with $n = 2k$ sides, in which $N_t(k) = 14620$ triangles can be formed, we have
  \gath{
    N_t(k) = 2k(k-1) = 14620 \non
    2k^2 - 2k - 14620 = 0 \non
    k^2 - k - 7310 = 0.
  }
  Solving this quadratic and taking the positive root, gives $k = 86$ so that our answer is $n = 2k = 2 \cdot 86 = 172$.
}

\aproblem{23}{396}{\advent@xxiii@xxiii}{
  Suppose that we have an $n$ by $n$ square.
  We focus not on the rectangles, but on the line segments that form them.
  In order for there to be three rectangles, there must two line segments, and at least one of them must go straight across the entire length of the square.
  If this were not the case, then we would have a section of the square that is not rectangular.
  So, first, consider the case where the two lines are both vertical across the entire square.
  As there are $n-1$ vertical positions within the square, there are of course
  \gath{
    N_v(n) = \combos{n-1}{2} = \binom{n-1}{2} = \frac{(n-1)!}{2!(n-1-2)!} = \frac{(n-1)!}{2(n-3)!} = \frac{(n-1)(n-2)}{2}
  }
  ways to choose two of them.
  There of course also $N_v(n)$ ways again in the analogous case in which both lines are horizontal instead.

  Now we turn our attention to the case in which the main line is vertical across the entire square and the other line is horizontal from either side of the square, stopping when it hits the main line.
  There are clearly $n-1$ ways to choose the main line.
  For each of these, then, there are $2(n-1)$ ways to choose the horizontal line since it can be on either side of the main vertical line.
  Thus, there are
  \gath{
    N_m(n) = (n-1) \cdot 2(n-1) = 2(n-1)^2
  }
  configurations of this case.
  This is again doubled to account for the analogous case when the main line is horizontal and the secondary line is vertical.

  Therefore, the total number of configurations is
  \ali{
    N(n) &= 2N_v(n) + 2N_m(n) = 2 \frac{(n-1)(n-2)}{2} + 2 \cdot 2(n-1)^2 \non
    &= (n-1)(n-2) + 4(n-1)^2 = (n-1)(n - 2 + 4(n-1)) \non
    &= (n-1)(n-2 + 4n - 4) = (n-1)(5n - 6).
  }
  This yields
  \gath{
    N(3) = (3-1)(5\cdot3 - 6) = 2(15-6) = 2 \cdot 9 = 18
  }
  as expected from the example.
  Our answer is of course then
  \gath{
    N(10) = (10-1)(5\cdot 10 - 6) = 9(50-6) = 9 \cdot 44 = 396.
  }
}

\aproblem{24}{107}{\advent@xxiii@xxiv}{
  Since we are interested only in three-digit numbers, we begin with $100$, which is $1100100$ in binary.
  In general, we want as many digits to be zero as possible as this decreases the number, since we are interested in minimizing the number.
  However, we cannot make the first two \mn{1} zero as this would drop the number below $100$ decimal so that it would no longer have three decimal digits.
  We like the two \mn{0} following the two \mn{1}, but these violate the required property of the binary representation, so we need to make one of them a $1$.
  Since it has a lower place value, we should change the second $0$ to a $1$ (the fourth binary digit) to get $1101100$.
  Since we have flipped this to a $1$, we are free to change any subsequent binary digits while still ensuring that we have a three-digit decimal number.
  Of course, our desired number needs to end in a $1$, so we can go ahead flip that bit to get $1101101$.
  This number does meet our requirements, but can be made smaller.
  Since the fourth digit is not $0$, we can decrease the fifth digit from a $1$ to a $0$ to get $1101001$, but now we have a double zero again.
  To remedy this, we simply change the next (i.e. the sixth) digit from a $0$ to a $1$ to get $1101011$.
  This is fact our minimal answer as there is no further way to decrease it by flipping any \mn{1} to \mn{0} without doing one of the following
  \begin{enumerate}[label=(a)]
    \item Making the decimal number only two digits.
    \item Making the binary number contain two \mn{0} in a row.
    \item Making the binary number not end in a $1$.
  \end{enumerate}
  Thus, our answer is the decimal representation of $1101011$, which is $107$.
  This was verified with a brute force Python program.
}

\end{document}
