\documentclass{article}
\input{common/prelude}

% Macros
\input{common/macros}
\input{questions}

\begin{document}

\title{Matthew Scroggs 2020 Christmas Card Solutions}
\author{Dan Whitman}
\date{}

\maketitle

Link to the online card: \href{https://www.mscroggs.co.uk/blog/87}{https://www.mscroggs.co.uk/blog/87}

\cproblem{1}{1304}{\card@xx@i}{
  The number of $r$-digit numbers formed using these digits is the number of permutations of the 6 digits, selecting $r$ of them.
  If interested only in the odd numbers, the least significant digit must only be chosen from the 4 odd digits (1, 3, 5, and 7) whereas the rest are chosen normally from the remaining digits.
  Thus the total number of odd numbers is reasoned to be
  \gath{
    \sum_{r=1}^5 \frac{4 \cdot 5!}{6 - r} = 1304 \,.
  }

  This answer was also verified using a brute force Python program.
}

\cproblem{2}{322402}{\card@xx@ii}{
Each sheet of paper has four numbers on it.
For example, the bottom sheet would have the numbers 1 and 2 on the front half and 161199 and 161200 on the back half.
In general, it is reasoned the that $n$th sheet, where the bottom is sheet 1, has the following numbers on it:
\ali{
  & 2n -1 &
  & 2n &
  & N - 2(n-1) - 1 &
  & N - 2(n-1) \,,
}
where $N = 161200$.
Therefore the sum of the numbers on the $n$th sheet is
\ali{
s_n &= [2n - 1] + [2n] + [N - 2(n-1) - 1] + [N - 2(n-1)] \non
&= 4n - 2 + 2N - 4(n-1) \non
&= 4n - 2 + 2N - 4n + 4 \non
&= 2N + 2 \non
&= 2(N+1) \non
&= 322402 \,.
}
So evidently all sheets have this same sum, which means that it is of course also the largest number since it is the only number!

This answer was also verified using a brute force Python program.
}

\cproblem{3}{4249475344}{\card@xx@iii}{
  Let $N = 65188$ so that $2N - 1 = 130375$ is clearly the largest odd number between these.
  The sum of all odd numbers between is then reasoned to be
  \ali{
    s &= \sum_{n=1}^N (2n - 1) = \sum_{n=1}^N 2n - \sum_{n=1}^N 1 = 2 \sum_{n=1}^N n - N \non
    &= 2 \frac{N(N+1)}{2} - N = N(N+1) - N = N^2 + N - N \non
    &= N^2 = 4249475344
  }

  This answer was also verified using a brute force Python program.
}

\cproblem{4}{51}{\card@xx@iv}{
  Suppose that the values on the the cards are $a$, $b$, and $c$.
  Then we have the following equations
  \ali{
    a + b &= 31 &
    a + c &= 35 &
    b + c &= 46 \,,
  }
  noting that it does not matter which of the variables corresponds to which card since there are only three.
  We then have that
  \gath{
    (a + b) + (a + c) + (b + c) = 31 + 35 + 46 = 102 \non
    2a + 2b + 2c = 102 \non
    2(a + b + c) = 102 \non
    a + b + c = 51
  }
  We could also solve the above system of linear equations directly using matrices:
  \gath{
    \begin{bmatrix}
      1 & 1 & 0 \\
      1 & 0 & 1 \\
      0 & 1 & 1
    \end{bmatrix}
    \begin{bmatrix}
      a \\ b \\ c
    \end{bmatrix}
    =
    \begin{bmatrix}
      31 \\ 35 \\ 36
    \end{bmatrix} \,.
  }
  This results in the numbers on the cards being $a = 15$, $b = 16$, and $c = 20$ so that again their sum is the same as before.
}

\cproblem{5}{4011}{\card@xx@v}{
  Suppose that the square base of the pyramid has sides $s$ and the pyramid has a height $h$.
  Then the formula for its volume, which we are given, is
  \gath{
    V_p = \frac{h s^2}{3} = 1337 \,.
  }
  Clearly the smallest cuboid containing the pyramid has dimensions of $s \times s \times h$ so that its volume is
  \gath{
    V_c = h s^2 \,.
  }
  Therefore
  \gath{
    \frac{V_c}{3} = \frac{h s^2}{3} = V_p \non
    V_c = 3 V_p = 4011 \,.
  }
}

\cproblem{6}{3355}{\card@xx@vi}{
  Letting $a = 305$ and $b = 671$, we have that $\gcd(a,b) = 61$.
  Hence the lowest common multiple is
  \gath{
    \lcm(a,b) = \frac{ab}{\gcd(a,b)} = 3355 \,.
  }
}

\cproblem{7}{2305}{\card@xx@vii}{
  For $n$ dice, the minimum possible sum is $n$ when they all roll a one.
  The maximum number is $6n$ when they all roll a six.
  Every sum $s$ such that $n \leq s \leq 6n$ is possible and occurs some number of times in the $6^n$ possible dice combinations.
  Obviously the sums $s = n$ and $s = 6n$ each occur only once.
  Let $N_n(s)$ be the number of combinations that sum $s$ occurs in the rolls of $n$ dice, which is of course directly related to the probability of that sum occurring.
  Though I was unable to prove it, some numerical experiments showed that all the values of $s$ are symmetric such that
  \gath{
    N_n(n + i) = N_n(6n - i)
  }
  for all integer $0 \leq i \leq 5n$.

  Letting $a = 6136$ and $b = 9999$, there must then be some integers $n$ and $i$ such that
  \ali{
    n + i &= a \\
    6n -i &= b
  }
  since these sums have the same probability.
  Thus this linear system can be solved:
  \gath{
    \begin{bmatrix}
      1 & 1  \\
      6 & -1
    \end{bmatrix}
    \begin{bmatrix}
      n \\ i
    \end{bmatrix}
    =
    \begin{bmatrix}
      a \\ b
    \end{bmatrix} \,.
  }
  Doing so results in $n = 2305$ and $i = 3830$, where of course $n$ is the number of dice and so is our answer.
}

\cproblem{8}{1225}{\card@xx@viii}{
For an $n \times m$ grid, it is reasoned that the number of different squares with sides of $k$ spaces is
\gath{
  N_k = (n - k + 1)(m - k + 1) \,,
}
assuming that $n \geq k$ and $m \geq k$ (where $N_k = 0$ otherwise since no $N_k$ squares can fit in the grid).
Letting $p = \min(n,m)$, it is reasoned that the total number of squares in the grid is
\ali{
N &= \sum_{k=1}^{p} N_k = \sum_{k=1}^p (n - k + 1)(m - k + 1) = \sum_{k=1}^p [n - (k - 1)][m - (k - 1)] \non
&= \sum_{k=0}^{p-1} (n - k)(m - k) = \sum_{k=0}^{p-1} \left[nm - k(n + m) + k^2\right] \non
&= nm \sum_{k=0}^{p-1} 1 - (n + m) \sum_{k=0}^{p-1} k + \sum_{k=0}^{p-1} k^2 \non
&= pnm - (n + m) \frac{p(p-1)}{2} + \frac{p(p-1)(2p-1)}{6} \non
&= pnm + \frac{p(p-1)}{6} \left(2p - 3n - 3m - 1\right)
}
noting that this formula is symmetric with respect to $n$ and $m$, which is to be expected.
In our case of course $n = 14$ and $m = 16$ so that $p = \min(14, 16) = 14$, which results in $N = 1225$.

The sum was also verified in its original form with Python.
}

\cproblem{9}{141516}{\card@xx@ix}{
  First, since the sum is odd, it has to be that the least significant digit was the one that was removed, since otherwise the last digit of the sum would be even.
  So, if $x$ is the original number and $d_0$ is its last digit, then the second number is
  \gath{
    y = \frac{x - d_0}{10} \,.
  }
  Hence the sum of these numbers is
  \gath{
    s = x + y = x + \frac{x - d_0}{10} = 155667 \non
    10x + x - d_0 = 10s \non
    11x = 10s + d_0 \,.
  }
  Hence we merely need to find the digit $d_0$ such that $10s + d_0$ is divisible by $11$, of which there are 10 possibilities since $d_0 \in \{0,1,\ldots,8,9\}$.
  This was checked using a Python program, which found that this condition is met only when $d_0 = 6$ so that the original number must be $x = (10s + d_0)/11 = 141516$.
}

\end{document}
