\documentclass{article}
\input{common/prelude}

% Macros
\input{common/macros}
\input{questions}

\begin{document}

\title{MS Scroggs 2022 Christmas Card Solutions}
\author{Dan Whitman}
\date{}

\maketitle

Link to the online card: \href{https://www.mscroggs.co.uk/blog/98}{https://www.mscroggs.co.uk/blog/98}

\cproblem{1}{5}{\card@xxii@i}{
  Just working through the primes starting at $1$, the answer is clearly $5$, which is two more than $3$ and two less than $7$, both of which are also prime.
}

\newcommand\sumo[1]{s_\mathrm{o}\parens{#1}}
\cproblem{2}{49}{\card@xxii@ii}{
  While this would be really simple to just manually calculate, it is more fun (though perhaps more work) to derive an easier formula.
  Clearly the sum of the first $n$ odd numbers is going to be
  \gath{
    \sumo{n} = \sum_{k=1}^n (2k - 1) = 2 \sum_{k=1}^n k - \sum_{k=1}^n 1 = \frac{2n(n+1)}{2} - n = n^2 \,.
  }
  Thus our answer is $\sumo{7} = 7^2 = 49$.
}

\cproblem{3}{33}{\card@xxii@iii}{
  From the equation derived in the previous problem, clearly the answer is $\sqrt{1089} = 33$.
}

\cproblem{4}{1}{\card@xxii@iv}{
  Since $7$ is prime, the quotient group $\ints/7\ints$ is cyclic, and indeed $4$ is a generator for it.
  From this it follows that \emph{any} integer can be obtained by adding only integer multiples of $4$ and $7$.
  As an example, clearly $2 \cdot 4 - 1 \cdot 7 = 1$, which is of course the smallest positive integer period.
}

\cproblem{5}{80}{\card@xxii@v}{
  This is similar to the previous problem, but not so straightforward because our two integers are not coprime.
  In particular, $\gcd(240, 400) = 80$ so that only integer multiples of $80$ are obtainable by adding integer multiples of $240$ and $400$.
  Hence, our answer is of course $80$, noting that $2 \cdot 240 - 1 \cdot 400 = 80$ as an example of how to attain this.
}

\cproblem{6}{20}{\card@xxii@vi}{
  Here we can leverage the solution of the 2022, Dec~6 problem.
  There, it was reasoned that, for a digital sum of $1 \leq s \leq 9$, the number of $m$-digit numbers with this digital sum and for which there are no nonzero digits is the recursive function
  \gath{
    N_m(s) = \begin{cases}
      1                             & m = 1         \\
      \sum_{j=m-1}^{s-1} N_{m-1}(j) & 1 < m \leq 9.
    \end{cases} \label{eqn:06:rec}
  }
  It was also derived that, in particular,
  \gath{
    N_3(s) = \frac{(s-1)(s-2)}{2}.
  }
  Hence, for $4$-digit numbers we have
  \ali{
    N_4(s) &= \sum_{j=3}^{s-1} N_3(j) = \sum_{j=3}^{s-1} \frac{(j-1)(j-2)}{2} = \frac{1}{2} \sum_{j=3}^{s-1} \parens{j^2 - 3j + 2} = \frac{1}{2} \parens{\sum_{j=3}^{s-1} j^2 - 3 \sum_{j=3}^{s-1} j + 2 \sum_{j=3}^{s-1} 1} \non
    &= \frac{1}{2}\squares{\frac{s(s-1)(2s-1)}{6} - (2^2 + 1^2) - \frac{3s(s-1)}{2} + 3(2 + 1) + 2(s-3)} \non
    &= \frac{1}{2}\squares{\frac{2s^3 - 12s^2 + 22s - 12}{6}} = \frac{s^3 - 6s^2 + 11s - 6}{6}.
  }
  So our answer is then $N_4(7) = 20$, which was also verified with a brute force search Python program.
}

\cproblem{7}{64}{\card@xxii@vii}{
  This is just like the previous problem except that we are looking at all positive integers instead of just the $4$-digit integers.
  Again, we can use the results of the 2022, Dec~6 problem, according to which this number for the general digital sum $s$ is
  \gath{
    N_s = \sum_{m=1}^s N_m(s). \label{eqn:07:Ns}
  }
  Just like the Dec~6 problem, we shall not undergo the tedium of computing $N_5(s)$, $N_6(s)$, or $N_7(s)$, but instead implement \eqref{eqn:07:Ns} along with the recursive function \eqref{eqn:06:rec} in Python to arrive at our answer $N_7 = 64$.
  As before, this result was also verified with a brute force search in the Python program.
}

\cproblem{8}{2836}{\card@xxii@viii}{
  Suppose that the original $4$-digit number has digits $d_3 d_2 d_1 d_0$, where of course $0 \leq d_i \leq 9$ for all $0 \leq i \leq 3$.
  Now, it \emph{has} to be that the least significant digit is the one that was removed since otherwise the sum would end in $d_0 + d_0 = 2d_0$ so that it would have to end in an even digit.
  Since the sum
  ends in a $9$ though, it must be that the $3$-digit number is $d_3 d_2 d_1$, and our sum is
  \begin{center}
    \begin{tabular}{ccccc}
          & $d_3$ & $d_2$ & $d_1$ & $d_0$ \\
      $+$ &       & $d_3$ & $d_2$ & $d_1$ \\
      \hline
          & 3     & 1     & 1     & 9
    \end{tabular}
  \end{center}
  Clearly either $d_3 = 3$ and nothing is carried from the $d_2 + d_3$ digit, or else $d_3 = 2$ and a $1$ \emph{is} carried.
  It must be the latter case since, in the former case, clearly $d_2 + d_3 = d_2 + 3 > 1$ so that this would have to be an $11$ instead and thus would carry, which contradicts that case.
  So, since $d_3 = 2$ and the previous digit's sum must be $11$, we have a similar situation in that either $d_2 = 9$ and there is no carry from the $d_1 + d_2$ digit, or else $d_2 = 8$ and there is a carry.
  For the same reason as before it must be that there \emph{is} a carry so that $d_2 = 8$.

  Now, there can be no carry from the least significant $d_0 + d_1$ digit because there is no way for this sum to reach $19$.
  Thus, we have that $d_1 + d_2 = d_1 + 8 = 11$ so that clearly $d_1 = 3$.
  Then of course $d_0 + d_1 = d_0 + 3 = 9$, and hence $d_0 = 6$.
  Therefore, the original number is $d_3 d_2 d_1 d_0 = 2836$, and indeed it is trivial to verify that $2836 + 283 = 3119$ as required.
}

\cproblem{9}{93079}{\card@xxii@ix}{
  Suppose that the original $5$-digit number has digits $d_4 d_3 d_2 d_1 d_0$, where of course $0 \leq d_i \leq 9$ for all $0 \leq i \leq 4$.
  Since we are looking for the largest original number, let us first explore the implications if the first digit is $d_4 = 9$ since the corresponding digit in the sum is $9$.
  Now, if $d_4$ is \emph{not} the digit that was removed in forming the $4$-digit number, then our sum is
  \begin{center}
    \begin{tabular}{cccccc}
          & $9$ & $d_3$ & $d_2$ & $d_1$ & $d_0$ \\
      $+$ &     & $9$   & ?     & ?     & ?     \\
      \hline
          & 9   & 6     & 1     & 5     & 8
    \end{tabular}
  \end{center}
  Here we reach a contradiction as there is no way for the sum of $d_3 + 9$ to be $6$ without carrying such that the next $d_4 = 9$ sum would not be $9$ as required.
  Thus, if $d_4 = 9$, then it must be that this \emph{is} the digit that was removed to form the second number.
  In this case our sum becomes
  \begin{center}
    \begin{tabular}{cccccc}
          & $9$ & $d_3$ & $d_2$ & $d_1$ & $d_0$ \\
      $+$ &     & $d_3$ & $d_2$ & $d_1$ & $d_0$ \\
      \hline
          & 9   & 6     & 1     & 5     & 8
    \end{tabular}
  \end{center}
  Here the remaining digits all line up so that each digital sum is normally $d_i + d_i = 2d_i$.
  So, their sum is odd if and only if there is a carry from the sum of the next lower digits, since  a carry always add $1$ to the sum, making it odd instead.

  So, since the $d_1$ sum is $5$, which is odd, it must be that $d_0 = 9$ instead of $4$ so that $d_0 + d_0 = 18$, which carries.
  The $d_2$ sum is also odd, which implies that $d_1 = 7$ instead of $2$ so that its sum is $d_1 + d_1 + 1 = 15$, which also carries.
  Now, the $d_3$ sum is $6$, which is even, so that $d_2 = 0$ so that its sum is $d_2 + d_2 + 1 = 1$ with no carry.
  Since we already concluded that the $d_3$ sum cannot carry, it must be that simply $d_3 = 3$.

  Putting this all together, our original $5$-digit number must be $d_4 d_3 d_2 d_1 d_0 = 93079$.
  Since this number was completely determined based only on setting $d_4 = 9$ with no arbitrary decisions along the way, this must be \emph{the} largest that the $5$-digit could have been since any other number would have to start with $d_4 = 8$ (with a carry from the previous digital sum).
  This result was verified with a brute force Python program.
}

\cproblem{10}{66}{\card@xxii@x}{
  In general, for $n$ points, since a line must connect every pair of distinct points, the number of lines is simply the number of combinations of choosing $2$ of the $n$ points, which is
  \gath{
    N(n) = \binom{n}{2} = \frac{n!}{2!(n-2)!} = \frac{n(n-1)}{2}.
  }
  As pointed out in the 2022, Dec~21 problem, these are the triangular numbers.
  In our case here, we simply have $N(12) = 12 \cdot 11 / 2 = 66$.
}

\cproblem{11}{77}{\card@xxii@xi}{
  Just as in the previous problem, for $n$ points, there are
  \gath{
    N(n) = \binom{n}{2} = \frac{n!}{2!(n-2)!} = \frac{n(n-1)}{2}
  }
  lines connecting each distinct pair of points.
  In this case, however, we know that $N(n) = 2926$ and need to find the corresponding $n$.
  Hence, we have
  \gath{
    N(n) = \frac{n(n-1)}{2} = 2926 \non
    n^2 - n = 5852 \non
    n^2 - n - 5852 = 0 \non
    (n - 77)(n + 76) = 0 \label{eqn:11:quad}
  }
  so that clearly $n = 77$ is the correct, positive solution so that $77$ points were drawn.
  Note that the final step of \eqref{eqn:11:quad} might seem magical, but the quadratic formula could just as easily have been used here.
}

\end{document}
